---
title: "BLH--Foutz"
author: "Dr. Riley M. Anderson"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
graphics: yes
output:
  github_document:
    toc: yes
    toc_depth: 5
    pandoc_args: --webtex
  html_document:
    keep_md: yes
    theme: readable
    mathjax: default
  html_notebook:
    code_folding: hide
    theme: readable
    mathjax: default
  pdf_document:
    toc: yes
header-includes:
  \usepackage{float}
  \floatplacement{figure}{H}
editor_options:
  chunk_output_type: console
---

```{r setup, include = F}
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
# @@@@@ Knitr Options
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@

# Set root directory to the project directory
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())


# Set default knitr options: 
# Suppress warnings and messages, cache chunks, 
#  set default figure size to 6x8 at 300 dpi, and save a png and pdf
knitr::opts_chunk$set(warning = F, message = F, collapse = T, cache = T,
    fig.height = 6, fig.width = 8, dpi = 300, # 6x8" @ 300dpi:1800x2400=4.3MP
    dev = c('png', 'pdf'), dev.args = list(pdf = list(onefile = F)))

```



## Overview

This markdown creates three figures for the Foutz et al. manuscript.


```{r Main_Code, include = F, cache = F}

# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
# @@@@@ Setup - This code is run, but output is hidden
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@

# Load Packages
library(tidyverse) # Needed for data wrangling: dplyr, tidyr, ggplot2
library(cowplot) # Needed for publication-quality ggplots
library(viridis)

# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
# @@@@@ Data Preparation
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@

# Import datasets
plants <- read.csv("data/JF_plants.csv")

blh <- read.csv("data/JF_blh.csv")

```


```{r Data_Wrangling_plants, echo = F, comment = ""}

## wrangling for the plant data:

plants1 <- plants %>% 
  mutate(
         # converting the excel date into a Date class:
         date = as.Date(date, origin = "1899-12-30"),
         
         # making the site, region, and host variables as factors:
         across(c(site : host), factor),
         
         # creating and factoring a column for `year` and `month`:
         Year = factor(year(date)),
         Month = factor(month(date)),
         
         # creating a co-infection variable automatically:
         co_inf = case_when(
           BLTVA_status == 1 &
             BCTV_status == 1 ~ 1,
           TRUE ~ 0
         ),
         
         # converting the infection "0,1" into a meaningful factor:
         BLTVA_status = factor(case_when(
           BLTVA_status == 1 ~ "infected",
           BLTVA_status == 0 ~ "healthy",
           TRUE ~ NA
         )),
         BCTV_status = factor(case_when(
           BCTV_status == 1 ~ "infected",
           BCTV_status == 0 ~ "healthy",
           TRUE ~ NA
         )),
         
         # removing typos:
         host = factor(case_when(
           host == "Tumble Mustard" ~
             "Tumble mustard",
           host == "Scotch thistle " ~ "Scotch thistle",
           host == "Netseed Lambsquarters" ~ "Netseed lambsquarters",
           TRUE ~ host
         )))

# which plants were most abundant?
count_plants <- plants1 %>% 
  
  # group the data by month and host plant:
  group_by(Month, host) %>% 
  
  # count the occurrences of each host plant/grouping:
  tally(name = "plant_count") %>% 
  
  # group by host plant and calculate the mean of occurrences: 
  group_by(host) %>% 
  summarise(M = mean(plant_count)) %>% 
  
  # sort the plants my descending mean occurrence:
  arrange(desc(M)) %>% 
  
  # take only the top 20th percentile:
  filter(M > quantile(M, 0.8))


# get the abundance and proportion infected (BLTVA):
bltva <- plants1 %>% 
  
  # count the occurrences of each infection status per month and host:
  group_by(Month, host, BLTVA_status) %>% 
  tally(name = "bltva") %>% 
  
  # widen the infection status to calculate prop. infected:
  pivot_wider(names_from = BLTVA_status,
              values_from = bltva,
              # fill any trimmed cell with a 0:
              values_fill = list(bltva = 0)) %>% 
  
  # calculate the total plants and proportion infected:
  mutate(total = healthy + infected,
         pr_bltva = infected/total) %>% 
  
  # return only hosts identified as the top 20th %tile in abundance:
  semi_join(., y = count_plants, by = "host") %>% 
  
  select(-healthy, -infected)


# get the abundance and proportion infected (BCTV):
bctv <- plants1 %>% 
  group_by(Month, host, BCTV_status) %>% 
  tally(name = "bctv") %>% 
  pivot_wider(names_from = BCTV_status,
              values_from = bctv,
              values_fill = list(bctv = 0)) %>% 
  mutate(total = healthy + infected,
         pr_bctv = infected/total) %>%  
  semi_join(., y = count_plants, by = "host") %>% 
  
  # remove redundant columns:
  select(host, Month, pr_bctv)

# join bltva and bctv props together:
plant_props <- left_join(bltva, bctv, by = c("Month", "host"))

```

# BLH plants

```{r BLH_plants, echo = F, fig.height = 4.8, fig.width = 11}

plant_order <- c("Pigweed", "Russian thistle", "Kochia",
                 "Potato", "Tumble mustard", "Flixweed")

pA <- plant_props %>% 
  ggplot(aes(x = Month,
             y = factor(host, level = plant_order),
             size = total, fill = pr_bltva)) +
  geom_point(shape = 21,
             color = 'black',
             show.legend = F) +
  scale_size(range = c(2, 20)) +
  theme_cowplot(font_size = 18) +
  theme(axis.title.y = element_blank(),
        strip.background = element_blank()) +
  scale_fill_viridis_c(option = "magma",
                       direction = -1) +
  labs(size = "No. plants",
       fill = "Pr(infected)") +
  annotate(geom = "text",
           label = "",
           y = 7, x = 1)

pB <- plant_props %>% 
  ggplot(aes(x = Month,
             y = factor(host, level = plant_order),
             size = total, fill = pr_bctv)) +
  geom_point(shape = 21,
             color = 'black') +
  scale_size(range = c(2, 20)) +
  theme_cowplot(font_size = 18) +
  theme(axis.title.y = element_blank(),
        strip.background = element_blank(),
        axis.text.y = element_blank()) +
  scale_fill_viridis_c(option = "magma",
                       direction = -1) +
  labs(size = "No. plants",
       fill = "Pr(infected)") +
  annotate(geom = "text",
           label = "",
           y = 7, x = 1)

plot_grid(pA, pB, labels = c("A", "B"),
          nrow = 1,
          label_x = c(.25, -0.025))

```

* **Figure 1.** Plants sampled and the proportion infected with **A)** BLTVA, and **B)** BCTV. Point size is proportional to the total plants sampled. Fill gradient continuously reflects proportion of infection, with light points representing less infection, and dark points representing more infection.

```{r Data_Wrangling_BLH, echo = F, comment = ""}

## wrangling for the BLH data:

blh1 <- blh %>% 
  mutate(
         # converting the excel date into a Date class:
         date = as.Date(date, origin = "1899-12-30"),
         
         # making the site, region, and host variables as factors:
         across(c(site : host, blh_lifestage), factor),
         
         # creating and factoring a column for `year` and `month`:
         Year = factor(year(date)),
         Month = factor(month(date)),
         
         # creating a co-infection variable automatically:
         co_inf = case_when(
           BLTVA_status == 1 &
             BCTV_status == 1 ~ 1,
           TRUE ~ 0
         ),
         
         # converting the infection "0,1" into a meaningful factor:
         BLTVA_status = factor(case_when(
           BLTVA_status == 1 ~ "infected",
           BLTVA_status == 0 ~ "healthy",
           TRUE ~ NA
         )),
         BCTV_status = factor(case_when(
           BCTV_status == 1 ~ "infected",
           BCTV_status == 0 ~ "healthy",
           TRUE ~ NA
         )),
         host = factor(case_when(
           host == "Blue Mustard" ~ "Blue mustard",
           host == "Common Purslane" ~ "Common purslane",
           host == "Netseed Lambsquarters" ~ "Netseed lambsquarters",
           TRUE ~ host
         )))



# which plants had the most BLH nymphs?
count_blh <- blh1 %>% 
  filter(blh_lifestage == "nymph") %>% 
  
  # group the data by month and host plant:
  group_by(Month, host) %>% 
  
  # count the occurrences of each host plant/grouping:
  tally(name = "nymphs") %>% 
  
  # group by host plant and calculate the mean of occurrences: 
  group_by(host) %>% 
  summarise(M = mean(nymphs)) %>% 
  
  # sort the plants my descending mean occurrence:
  arrange(desc(M)) %>% 
  
  # take only the top 60th percentile:
  filter(M > quantile(M, 0.4))



### BLH NYMPHS -------------------------------

# NYMPHS -- get the abundance and proportion infected (BLTVA):
blh_bltva_nymph <- blh1 %>% 
  filter(blh_lifestage == "nymph") %>% 
  
  # count the occurrences of each infection status per month and host:
  group_by(Month, host, BLTVA_status) %>% 
  tally(name = "bltva") %>% 
  
  # widen the infection status to calculate prop. infected:
  pivot_wider(names_from = BLTVA_status,
              values_from = bltva,
              # fill any trimmed cell with a 0:
              values_fill = list(bltva = 0)) %>% 
  
  # calculate the total plants and proportion infected:
  mutate(total = healthy + infected,
         pr_bltva = infected/total) %>% 
  
  # return only hosts identified as the top 20th %tile in abundance:
  semi_join(., y = count_blh, by = "host")


# NYMPHS -- get the abundance and proportion infected (BCTV):
blh_bctv_nymph <- blh1 %>% 
  filter(blh_lifestage == "nymph") %>% 
  group_by(Month, host, BCTV_status) %>% 
  tally(name = "bctv") %>% 
  pivot_wider(names_from = BCTV_status,
              values_from = bctv,
              values_fill = list(bctv = 0)) %>% 
  mutate(total = healthy + infected,
         pr_bctv = infected/total) %>%  
  semi_join(., y = count_blh, by = "host") %>% 
  
  # remove redundant columns:
  select(host, Month, pr_bctv)

# join bltva and bctv props together:
blh_nymph_props <- left_join(blh_bltva_nymph, blh_bctv_nymph,
                             by = c("Month", "host"))



### BLH ADULTS -------------------------------

# which plants had the most BLH adults?
count_blh_adults <- blh1 %>% 
  filter(blh_lifestage != "nymph") %>% 
  
  # group the data by month and host plant:
  group_by(Month, host) %>% 
  
  # count the occurrences of each host plant/grouping:
  tally(name = "adults") %>% 
  
  # group by host plant and calculate the mean of occurrences: 
  group_by(host) %>% 
  summarise(M = sum(adults)) %>% 
  
  # sort the plants my descending mean occurrence:
  arrange(desc(M)) %>% 
  filter(M >= 15,
         host != "Mustard")

# ADULTS -- get the abundance and proportion infected (BLTVA):
blh_bltva_adult <- blh1 %>% 
  filter(blh_lifestage != "nymph") %>% 
  
  # count the occurrences of each infection status per month and host:
  group_by(Month, host, BLTVA_status) %>% 
  tally(name = "bltva") %>% 
  
  # widen the infection status to calculate prop. infected:
  pivot_wider(names_from = BLTVA_status,
              values_from = bltva,
              # fill any trimmed cell with a 0:
              values_fill = list(bltva = 0)) %>% 
  
  # calculate the total plants and proportion infected:
  mutate(total = healthy + infected,
         pr_bltva = infected/total) %>% 
  
  # return only hosts identified as the top 20th %tile in abundance:
  semi_join(., y = count_blh_adults, by = "host")


# ADUlTS -- get the abundance and proportion infected (BCTV):
blh_bctv_adult <- blh1 %>% 
  filter(blh_lifestage != "nymph") %>% 
  group_by(Month, host, BCTV_status) %>% 
  tally(name = "bctv") %>% 
  pivot_wider(names_from = BCTV_status,
              values_from = bctv,
              values_fill = list(bctv = 0)) %>% 
  mutate(total = healthy + infected,
         pr_bctv = infected/total) %>%  
  semi_join(., y = count_blh_adults, by = "host") %>% 
  
  # remove redundant columns:
  select(host, Month, pr_bctv)

# join bltva and bctv props together:
blh_adult_props <- left_join(blh_bltva_adult, blh_bctv_adult,
                             by = c("Month", "host"))

```


# BLH nymphs

```{r BLH_nymphs, echo = F, fig.height = 4.6, fig.width = 11}

blh_nymph_order <- c("Kochia", "Loesel's mustard", "Flixweed",
               "Tumble mustard", "Blue mustard")

nA <- blh_nymph_props %>% 
  ggplot(aes(x = Month,
             y = factor(host, level = blh_nymph_order),
             size = total, fill = pr_bltva)) +
  geom_point(shape = 21,
             color = 'black',
             show.legend = F) +
  scale_size(range = c(2, 20)) +
  theme_cowplot(font_size = 18) +
  theme(axis.title.y = element_blank()) +
  scale_fill_viridis_c(option = "magma",
                       limits = c(0, 0.1),
                       direction = -1) +
  annotate(geom = "text",
           x = 1, y = 6,
           label = "")

nB <- blh_nymph_props %>% 
  ggplot(aes(x = Month,
             y = factor(host, level = blh_nymph_order),
             size = total, fill = pr_bctv)) +
  geom_point(shape = 21,
             color = 'black') +
  scale_size(range = c(2, 20)) +
  theme_cowplot(font_size = 18) +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank()) +
  labs(size = "No. BLH",
       fill = "Pr(infected)") +
  scale_fill_viridis_c(option = "magma",
                       direction = -1) +
  annotate(geom = "text",
           x = 1, y = 6,
           label = "")


plot_grid(nA, nB, labels = c("A", "B"),
          rel_widths = c(1, 1),
          nrow = 1,
          label_x = c(0.25, -0.05))

```

* **Figure 2.** Plants sampled and the proportion infected with **A)** BLTVA, and **B)** BCTV. Point size is proportional to the total no. of beet leafhopper nymphs sampled. Fill gradient continuously reflects proportion of infection, with light points representing less infection, and dark points representing more infection.


# BLH adults

```{r BLH_adults, echo = F, fig.height = 5, fig.width = 12}

blh_adult_order <- c("Silver sagebrush", "Pigweed", "Netseed lambsquarters",
                     "Kochia", "Russian thistle", "Grasses",
                     "Potato", "Tumble mustard", "Flixweed")

aA <- blh_adult_props %>% 
  ggplot(aes(x = Month,
             y = factor(host, level = blh_adult_order),
             size = total, fill = pr_bltva)) +
  geom_point(shape = 21,
             color = 'black',
             show.legend = F) +
  scale_size(range = c(2, 20)) +
  theme_cowplot(font_size = 18) +
  theme(axis.title.y = element_blank()) +
  scale_fill_viridis_c(option = "magma",
                       limits = c(0, 0.5),
                       direction = -1) +
  annotate(geom = "text",
           x = 1, y = 10,
           label = "")

aB <- blh_adult_props %>% 
  ggplot(aes(x = Month,
             y = factor(host, level = blh_adult_order),
             fill = pr_bctv, size = total)) +
  geom_point(shape = 21,
             color = 'black') +
  scale_size(range = c(2, 20),
             breaks = c(10, 50, 150, 250)) +
  theme_cowplot(font_size = 18) +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank()) +
  labs(fill = "Pr(infected)",
       size = "No. BLH") +
  scale_fill_viridis_c(option = "magma",
                       direction = -1) +
  annotate(geom = "text",
           x = 1, y = 10,
           label = "") +
  guides(fill = guide_colorbar(order = 1),
         size = guide_legend(order = 2))


plot_grid(aA, aB, labels = c("A", "B"),
          rel_widths = c(1.1, 1),
          nrow = 1,
          label_x = c(0.25, -0.05))

```

* **Figure 3.** Plants sampled and the proportion infected with **A)** BLTVA, and **B)** BCTV. Point size is proportional to the total no. of beet leafhopper adults sampled. Fill gradient continuously reflects proportion of infection, with light points representing less infection, and dark points representing more infection.




## Session Information

```{r Session_Info, echo = F, comment = ""}

# Add session information to help with reproduceability
sessionInfo()


```


