---
title: "Camille's BLH Analysis V1"
author: "Riley M. Anderson & Camille Wagstaff"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
graphics: yes
output:
  github_document:
    toc: yes
    toc_depth: 5
    pandoc_args: --webtex
  html_document:
    keep_md: yes
    theme: readable
    mathjax: default
  html_notebook:
    code_folding: hide
    theme: readable
    mathjax: default
  pdf_document:
    toc: yes
header-includes:
  \usepackage{float}
  \floatplacement{figure}{H}
editor_options:
  chunk_output_type: console
---

```{r setup, include = F}
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
# @@@@@ Knitr Options
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@

# Set root directory to the project directory
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())


# Set default knitr options: 
# Suppress warnings and messages, cache chunks, 
#  set default figure size to 6x8 at 300 dpi, and save a png and pdf
knitr::opts_chunk$set(warning = F, message = F, collapse = T, cache = T,
    fig.height = 6, fig.width = 8, dpi = 300, # 6x8" @ 300dpi:1800x2400=4.3MP
    dev = c('png', 'pdf'), dev.args = list(pdf = list(onefile = F)))

```



## Overview

Camille's beet leafhopper project.

When (seasonal) and where (plants/regions?) do BCTV infections come from?

Is virus positive predictive of diet? Difference in diet based on infection?

### Summary of Results
* 

```{r Main_Code, include = F, cache = F}

# Load Packages
library(tidyverse) # Needed for data wrangling: dplyr, tidyr, ggplot2
library(cowplot) # Needed for publication-quality ggplots
library(sjPlot)
library(lubridate)

# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
# @@@@@ Data preparation
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@

# Import datasets
d19 <- read.csv("data/camille.2019.csv")

d20 <- read.csv("data/camille.2020.csv")

d21 <- read.csv("data/2021 BLH GCA.csv")



```


```{r Data_Wrangling, echo = F, comment = ""}

# matching 2019 colnames to 2020 & 2021

d19 <- d19 %>% 
  rename(BarCode = Barcode,
         Date = Collection.Date,
         Host.Plant = Plant.BLH.collected.from)

# bring the 3 years together

dat1 <- bind_rows(d19, d20, d21)


# variable structure

dat1 <- dat1 %>% 
  mutate(Date = ymd(dat1$Date)) %>% 
  mutate(across(
    c(Plant.Type, Family, Genus,
      BLH, Host.Plant, Region,
      Site, Time.Period), as.factor)) %>% 
  mutate(Year = lubridate::year(Date),
         BLH.year = factor(paste(BLH, Year, sep = "_"))) %>% 
  filter(BLH != 0)





# dat1 <- dat1 %>% 
#   mutate(Plant.Type = case_when(
#     Common.Name == 'Tarragon' ~ 'Crop'
#   )) %>% 
#   mutate(Family = case_when(
#     Common.Name == 'Tarragon' ~ 'Asteraceae'
#   )) %>% 
#   mutate(
#     Host.Plant = case_when(
#       Host.Plant == 'Blue mustard' ~ 'Mustard',
#       Host.Plant == 'Flixweed/Pinnate tansymustard' ~ 'Tansymustard',
#       Host.Plant == 'Flixweed' ~ 'Tansymustard',
#       Host.Plant == 'Loesels mustard' ~ 'Mustard',
#       Host.Plant == 'Netseed LambsquaRussian thistleers' ~ 'Lambsquarter'
#     )
#   )
# 
# levels(dat1$Host.Plant)

```

# Exploratory Data Analysis

### BCTV by plant type (weed, crop, shrub, etc.)
```{r planttype_by_BCTV, echo = F}


dat1 %>% 
  select(BCTV, Plant.Type) %>% 
  group_by(BCTV, Plant.Type) %>% 
  summarise(count = n()) %>% 
  filter(!is.na(BCTV)) %>% 
  mutate(BCTV = factor(BCTV)) %>% 
  ggplot(aes(x = Plant.Type, y = count, fill = BCTV)) +
  geom_col() +
  theme_classic() +
  coord_flip()

```


### BCTV by plant type and year
```{r planttype_by_BCTV_year, echo = F}


dat1 %>% 
  select(BCTV, Plant.Type, Year) %>% 
  mutate(year = factor(Year)) %>% 
  group_by(BCTV, Plant.Type, Year) %>% 
  summarise(count = n()) %>% 
  filter(!is.na(BCTV)) %>% 
  mutate(BCTV = factor(BCTV)) %>% 
  ggplot(aes(x = Plant.Type, y = count, fill = BCTV)) +
  geom_col() +
  theme_classic() +
  facet_wrap(~ Year) +
  coord_flip()

```


### BCTV by family
```{r family_by_BCTV, echo = F}


dat1 %>% 
  select(BCTV, Family) %>% 
  group_by(BCTV, Family) %>% 
  summarise(count = n()) %>% 
  filter(!is.na(BCTV)) %>% 
  mutate(BCTV = factor(BCTV)) %>% 
  ggplot(aes(x = Family, y = count, fill = BCTV)) +
  geom_col() +
  theme_classic() +
  coord_flip()

```

### BCTV by genus
```{r genus_by_BCTV, echo = F}


dat1 %>% 
  select(BCTV, Genus) %>% 
  group_by(BCTV, Genus) %>% 
  summarise(count = n()) %>% 
  filter(!is.na(BCTV)) %>% 
  mutate(BCTV = factor(BCTV)) %>% 
  ggplot(aes(x = Genus, y = count, fill = BCTV)) +
  geom_col() +
  theme_classic() +
  coord_flip()

```

### BCTV by year
```{r year_by_BCTV, echo = F}


dat1 %>% 
  select(BCTV, Year) %>% 
  mutate(Year = factor(Year)) %>% 
  group_by(BCTV, Year) %>% 
  summarise(count = n()) %>% 
  filter(!is.na(BCTV)) %>% 
  mutate(BCTV = factor(BCTV)) %>% 
  ggplot(aes(x = Year, y = count, fill = BCTV)) +
  geom_col() +
  theme_classic()

```


### BCTV by time of year (all years together)
```{r timeperiod_by_BCTV, echo = F, cache = F}


dat1 %>% 
  select(BCTV, Time.Period) %>% 
  group_by(BCTV, Time.Period) %>% 
  summarise(count = n()) %>% 
  filter(!is.na(BCTV)) %>% 
  mutate(BCTV = factor(BCTV)) %>% 
  ggplot(aes(x = Time.Period, y = count, fill = BCTV)) +
  geom_col() +
  theme_classic() +
  scale_x_discrete(limits = c(
    "Late March", "Early April", "Late April", "Early May", "Late May",
    "Early June", "Late June", "Early July", "Late July", "Early August",
    "Late August", "Early October", "Late October"
  )) +
  labs(x = "Time period\nearly      ----->       late") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```


### BCTV by host plant (plant the BLH were collected from)
```{r hostplant_by_BCTV, echo = F}


dat1 %>% 
  select(BCTV, Host.Plant) %>% 
  group_by(BCTV, Host.Plant) %>% 
  summarise(count = n()) %>% 
  filter(!is.na(BCTV)) %>% 
  mutate(BCTV = factor(BCTV)) %>% 
  ggplot(aes(x = Host.Plant, y = count, fill = BCTV)) +
  geom_col() +
  theme_classic() +
  coord_flip()

```

### BCTV by gut richness 

```{r BCTV_gut_richness, echo = F}

BCTV <- dat1 %>% 
  filter(BLH != 0) %>% 
  group_by(BLH.year, BCTV) %>% 
  summarise(p_sp = n()) %>% 
  rename(infect = BCTV) %>% 
  filter(infect != "NA")

model_CTV_2 <- glm(infect ~ p_sp,
                   data = BCTV,
                   family = binomial)
summary(model_CTV_2)

BCTV %>% 
  ggplot(aes(x = p_sp, y = infect)) +
  geom_jitter(height = .03, shape = 1) +
  geom_smooth(method = "glm",
              method.args = list(family = "binomial"),
              color = 'black',
              alpha = .3) +
  theme_classic() +
  labs(x = "Gut richness",
       y = "Pr(BCTV infection)")


```


Gut content species richness significantly predicts BCTV infection. The odds of BCTV infection decrease by `r round(100*(1-exp(coef(model_CTV_2)[[2]])), 1)` % for every 1 species increase (*p* = `r round(summary(model_CTV_2)$coefficients[2,4], 3)`).




## Session Information

```{r Session_Info, echo = F, comment = ""}

# Add session information to help with reproduceability
sessionInfo()


```


