---
title: "Gut Contents from Hemp, Hops, and Carrot"
author: "Dr. Riley M. Anderson"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
graphics: yes
output:
  github_document:
    toc: yes
    toc_depth: 5
    pandoc_args: --webtex
  html_document:
    keep_md: yes
    theme: readable
    mathjax: default
  html_notebook:
    code_folding: hide
    theme: readable
    mathjax: default
  pdf_document:
    toc: yes
header-includes:
  \usepackage{float}
  \floatplacement{figure}{H}
editor_options:
  chunk_output_type: console
---

```{r setup, include = F}
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
# @@@@@ Knitr Options
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@

# Set root directory to the project directory
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())


# Set default knitr options: 
# Suppress warnings and messages, cache chunks, 
#  set default figure size to 6x8 at 300 dpi, and save a png and pdf
knitr::opts_chunk$set(warning = F, message = F, collapse = T, cache = T,
    fig.height = 5, fig.width = 10, dpi = 300, # 6x8" @ 300dpi:1800x2400=4.3MP
    dev = 'png', dev.args = list(pdf = list(onefile = F)))

```



## Overview

Multivariate analyses of Camille's potato/hemp/hops/carrot BLH gut contents.

### Summary of Results

* Plant species composition in the gut contents of BLH is weakly tied to sampling date (the grey contours in the NMDS figures).

* The predictors, **region**, and **BCTV** help explain some variation but do not differentiate gut composition. 

* **Host plant** was used as a block effect (random intercept and permutation stratification) in the models.

* The relationship with sampling date is convoluted and highly non-linear. I suspect this has much to do with the sampling across multiple years where regions were not sampled every year, or sampled at different times across years.

* The benchmark plant *Solanum*, for standardizing primer efficiency stands out by an order of magnitude. To me, this suggests that **sequences** are not representative of concentration in the gut. Instead, **sequences** are a function of primer efficiency. If so, this entire analysis should be ignored, as the ordinations are built from the assumption that **sequences** are at least partially a function of concentration in the gut.


```{r Main_Code, include = F, cache = F}

# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
# @@@@@ Setup - This code is run, but output is hidden
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@

# Load Packages
library(tidyverse) # Needed for data wrangling: dplyr, tidyr, ggplot2
library(cowplot) # Needed for publication-quality ggplots
library(vegan)
library(randomForest)
library(sjPlot)
library(ggrepel)
library(mgcv)

# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
# @@@@@ Data Preparation
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@

# Import datasets
dat1 <- read.csv("data/BLH_gut_contents_2025.csv")

dat1 <- read.csv("data/gut_contents_full.csv")


set.seed(123)
```


```{r Data_Wrangling, echo = F, comment = ""}

dat1 <- dat1 %>% 
  filter(!is.na(BCTV)) %>% 
  mutate(Date = as.Date(Date, origin = "1899-12-30"),
         extraction_date = as.Date(extraction_date,
                                   origin = "1899-12-30"),
         across(c(BLH_ID, type, family, common_name, Terpene,
                genus, organism, primer, time_period,
                region, site_name, host_plant, BCTV), factor),
         Terpene = factor(case_when(
           Terpene == "" ~ "none",
           Terpene == "None" ~ "none",
           TRUE ~ Terpene
         ))) %>% 
  # removing host_plants with few records:
  filter(host_plant != "Filaree" &
           host_plant != "Lambsquarter" &
           host_plant != "Mustard") %>% 
  droplevels() %>% 
  # correcting typos in time_period
  mutate(time_period = case_when(
    time_period == " August" ~ "August",
    time_period == " April" ~ "April",
    time_period == " July" ~ "July",
    time_period == " June" ~ "June",
    time_period == " March" ~ "March",
    time_period == " May" ~ "May",
    time_period == " October" ~ "October",
    TRUE ~ time_period),
         time_period = factor(time_period,
                              levels = c("March", "April", "May",
                                         "June", "July", "August",
                                         "October")))



meta <- dat1 %>% 
  select(BLH_ID, time_period, Date, extraction_date,
         region, host_plant, BCTV, Terpene, Year) %>% 
  distinct()

## Matrix and species by "Crop type":

species_counts <- dat1 %>%
  filter(!is.na(Sequences)) %>% 
  mutate(stan_seqs = Sequences / blh_mix_count,
         stan_seqs = round(stan_seqs, 0)) %>% 
  uncount(stan_seqs) %>% 
  select(BLH_ID, type) %>%
  group_by(BLH_ID, type) %>%
  tally(name = "Sequences") %>% 
  group_by(type) %>% 
  summarise(total_counts = sum(Sequences))

gut_matrix <- dat1 %>%
  filter(!is.na(Sequences)) %>% 
  mutate(stan_seqs = Sequences / blh_mix_count,
         stan_seqs = round(stan_seqs, 0)) %>% 
  uncount(stan_seqs) %>% 
  select(BLH_ID, type) %>%
  group_by(BLH_ID, type) %>%
  tally(name = "Sequences") %>% 
  pivot_wider(names_from = type,
              values_from = Sequences,
              values_fill = list(Sequences = 0)) %>% 
  left_join(., meta, by = "BLH_ID") %>% 
  mutate(sample_date = yday(Date),
         ex_date = yday(extraction_date)) %>% 
  select(-Date, -extraction_date)


## Matrix and species by "Genus"

genus_counts <- dat1 %>%
  filter(!is.na(Sequences)) %>% 
  mutate(stan_seqs = Sequences / blh_mix_count,
         stan_seqs = round(stan_seqs, 0)) %>% 
  uncount(stan_seqs) %>% 
  select(BLH_ID, genus) %>%
  group_by(BLH_ID, genus) %>%
  tally(name = "Sequences") %>% 
  group_by(genus) %>% 
  summarise(total_counts = sum(Sequences)) %>% 
  arrange(desc(total_counts)) %>% 
  filter(total_counts > quantile(total_counts, .8),
         genus != "Glycine")


gut_genus_matrix <- dat1 %>%
  filter(!is.na(Sequences)) %>% 
  mutate(stan_seqs = Sequences / blh_mix_count,
         stan_seqs = round(stan_seqs, 0)) %>% 
  uncount(stan_seqs) %>% 
  select(BLH_ID, genus) %>%
  group_by(BLH_ID, genus) %>%
  tally(name = "Sequences") %>% 
  semi_join(., genus_counts, by = "genus") %>% 
  pivot_wider(names_from = genus,
              values_from = Sequences,
              values_fill = list(Sequences = 0)) %>% 
  left_join(., meta, by = "BLH_ID") %>% 
  mutate(sample_date = yday(Date),
         ex_date = yday(extraction_date)) %>% 
  select(-Date, -extraction_date)
  


```

## NMDS by crop type
```{r NMDS_calcs_CropType, echo = F}

gut_ord <- gut_matrix %>% ungroup() %>% 
  select(Cannabis : Kochia) %>% 
  metaMDS(., k = 3, distance = "bray",
          trymax = 50, maxit = 1000)
## stress is acceptable with 3 dimensions
gut_ord$stress
stressplot(gut_ord)

# checking for trends with envfit():

gut_mod_envfit <- envfit(gut_ord ~ sample_date +
                           host_plant + BCTV,
                         strata = gut_matrix$region,
                         choices = c(1:3), na.rm = TRUE,
                         data = gut_matrix, nperm = 999)

gut_mod_envfit # Only sample date matters

gut_mod_envfit1 <- envfit(gut_ord ~ sample_date + BCTV +
                           host_plant + region,
                         choices = c(1:3), na.rm = TRUE,
                         data = gut_matrix, nperm = 999)

gut_mod_envfit1 # Region appears to have strong effects,
                # consider region as a fixed effect.

## checking for trends with GAM:

gut_mat_gam <- bind_cols(gut_matrix, scores(gut_ord)$sites)

gut_gam1 <- gam(sample_date ~ s(NMDS1, NMDS2, NMDS3, k = 9) +
                  region + BCTV + host_plant,
                  data = gut_mat_gam)

summary(gut_gam1) # Sample date has strong relationship

#### checking for trends with PERMANOVA:

gut_mat_species <- gut_matrix %>% ungroup() %>% 
  select(Cannabis : Kochia)

gut_mat_predictors <- gut_matrix %>% ungroup() %>% 
  select(-Cannabis : -Kochia)

# linear fit with samples date:
gut_ord_adonis1 <- adonis2(gut_mat_species ~
                            sample_date + BCTV +
                            host_plant + region,
                          data = gut_matrix)


# linear fit with samples date and region stratified:
gut_ord_adonis2 <- adonis2(gut_mat_species ~
                            sample_date + BCTV +
                            host_plant,
                           strata = gut_matrix$region,
                          data = gut_matrix)

# checking for non-linearity in sample date
gut_ord_adonis3 <- adonis2(gut_mat_species ~
                            splines::ns(sample_date, df = 3) +
                            host_plant + region + BCTV,
                          data = gut_matrix)

# checking for non-linearity in sample date with stratified region
gut_ord_adonis4 <- adonis2(gut_mat_species ~
                            splines::ns(sample_date, df = 3) +
                            host_plant+ BCTV,
                           strata = gut_matrix$region,
                          data = gut_matrix)

# relationship between sample date and gut contents is non-linear.

```


```{r gut_sample_date_figure_prep, echo = F}


gut_sites <- data.frame(scores(gut_ord)$sites) %>% 
  rownames_to_column("sample_num") %>% 
  bind_cols(., gut_mat_predictors)

gut_host_centroids <- gut_sites %>% 
  group_by(host_plant) %>% 
  summarise(NMDS1 = mean(NMDS1),
            NMDS2 = mean(NMDS2)) 

gut_ord_sample_date <- gam(sample_date ~ s(NMDS1, NMDS2, k = 9),
                       data = gut_sites)

summary(gut_ord_sample_date)

preddat <- expand.grid(NMDS1 = seq(-2.5, 2.5, 0.5),
                       NMDS2 = seq(-1.5, 2.2, 0.5))
preddat$date_pred <- predict(gut_ord_sample_date,
                                 newdata = preddat)




gut_species <- data.frame(scores(gut_ord)$species) %>% 
  rownames_to_column("type")

gut_species$date_centroid <- exp(predict(
  gut_ord_sample_date, newdata = gut_species))



gut_species <- gut_species %>% 
  left_join(., species_counts, by = "type")

```

### Crop type by field plant

```{r gut_sample_date_host_fig, echo = F}

ggplot(mapping = aes(x = NMDS1, y = NMDS2)) +
  geom_contour(data = preddat,
               aes(z = date_pred), color = "grey") +
  metR::geom_text_contour(data = preddat,
                          aes(z = date_pred),
                          color = "grey", stroke = 0.15, skip = 1) +
  geom_text_repel(data = gut_species, max.overlaps = 15,
                  aes(label = type, size = total_counts)) +
  scale_size_binned(transform = "log10", range = c(1.5, 5),
             breaks = c(3, 30, 300)) +
  theme_cowplot() +
  stat_ellipse(data = gut_sites,
               aes(x = NMDS1, y = NMDS2, color = host_plant)) +
  geom_point(data = gut_host_centroids,
             aes(x = NMDS1, y = NMDS2, fill = host_plant),
             shape = 21, size = 5, show.legend = F) +
  # geom_point(data = bee_sites,
  #            aes(x = NMDS1, y = NMDS2, color = period),
  #            show.legend = F) +
  labs(size = "Abundance",
       color = "Host plant") 

```

### Crop type by regions

```{r gut_sample_date_region_fig, echo = F}

gut_region_centroids <- gut_sites %>% 
  group_by(region) %>% 
  summarise(NMDS1 = mean(NMDS1),
            NMDS2 = mean(NMDS2))

ggplot(mapping = aes(x = NMDS1, y = NMDS2)) +
  geom_contour(data = preddat,
               aes(z = date_pred), color = "grey") +
  metR::geom_text_contour(data = preddat,
                          aes(z = date_pred),
                          color = "grey", stroke = 0.15, skip = 1) +
  geom_text_repel(data = gut_species, max.overlaps = 15,
                  aes(label = type, size = total_counts)) +
  scale_size_binned(transform = "log10", range = c(1.5, 5),
             breaks = c(3, 30, 300)) +
  theme_cowplot() +
  stat_ellipse(data = gut_sites,
               aes(x = NMDS1, y = NMDS2, color = region)) +
  geom_point(data = gut_region_centroids,
             aes(x = NMDS1, y = NMDS2, fill = region),
             shape = 21, size = 5, show.legend = F) +
  # geom_point(data = bee_sites,
  #            aes(x = NMDS1, y = NMDS2, color = period),
  #            show.legend = F) +
  labs(size = "Abundance",
       color = "Region")


```


### Crop type by BCTV

```{r gut_sample_date_BCTV_fig, echo = F}

gut_bctv_centroids <- gut_sites %>% 
  group_by(BCTV) %>% 
  summarise(NMDS1 = mean(NMDS1),
            NMDS2 = mean(NMDS2)) 

ggplot(mapping = aes(x = NMDS1, y = NMDS2)) +
  geom_contour(data = preddat,
               aes(z = date_pred), color = "grey") +
  metR::geom_text_contour(data = preddat,
                          aes(z = date_pred),
                          color = "grey", stroke = 0.15, skip = 0) +
  geom_text_repel(data = gut_species, max.overlaps = 15,
                  aes(label = type, size = total_counts)) +
  scale_size_binned(transform = "log10", range = c(1.5, 5),
             breaks = c(3, 30, 300)) +
  theme_cowplot() +
  stat_ellipse(data = gut_sites,
               aes(x = NMDS1, y = NMDS2, color = BCTV)) +
  geom_point(data = gut_bctv_centroids,
             aes(x = NMDS1, y = NMDS2, fill = BCTV),
             shape = 21, size = 5, show.legend = F) +
  # geom_point(data = bee_sites,
  #            aes(x = NMDS1, y = NMDS2, color = period),
  #            show.legend = F) +
  labs(size = "Abundance",
       color = "BCTV",
       x = "NMDS1",
       y = "NMDS2") +
  scale_color_manual(values = c("#009E73",
                                "#CC79A7")) +
  scale_fill_manual(values = c("#009E73",
                                "#CC79A7"))


```

## NMDS by genus
```{r NMDS_calcs_genus, echo = F, cache=F}

gut_ord_genus <- gut_genus_matrix %>% ungroup() %>% 
  select(Cannabis : Ulmus) %>% 
  metaMDS(., k = 3, distance = "bray",
          trymax = 50, maxit = 1000)
## stress is fine with 3 dimensions


stressplot(gut_ord_genus)
plot(gut_ord_genus)
# checking for trends with envfit():

gut_genus_matrix <- gut_genus_matrix %>% 
  mutate(Year = factor(Year))

genus_mod_envfit <- envfit(gut_ord_genus ~ sample_date +
                           region + BCTV + Year,
                         strata = gut_genus_matrix$host_plant,
                         choices = c(1:3),
                         data = gut_genus_matrix, nperm = 999)

genus_mod_envfit # Only sample date matters



## checking for trends with GAM:
library(gamm4)
genus_mat_gam <- bind_cols(gut_genus_matrix,
                           scores(gut_ord_genus)$sites)

genus_gam1 <- gamm4(sample_date ~ s(NMDS1, NMDS2, NMDS3),
                  random = ~(1 | host_plant),
                  data = genus_mat_gam)

summary(genus_gam1$gam) # Sample date has strong relationship
plot(genus_gam1$gam)


genus_gam2 <- gamm4(sample_date ~ s(NMDS1, NMDS2),
                  random = ~(1 | host_plant),
                  data = genus_mat_gam)

summary(genus_gam2$gam) # Sample date has strong relationship
plot(genus_gam2$gam)

##@@@

genus_mat_gam <- genus_mat_gam %>% 
  mutate(year_time = case_when(
    Year == "2019" ~ sample_date,
    Year == "2020" ~ sample_date + 365,
    Year == "2021" ~ sample_date + (2*365),
    Year == "2022" ~ sample_date + (3*365),
    TRUE ~ NA
  ))

genus_gam3 <- gamm4(year_time ~ s(NMDS1, NMDS2) + Year,
                  random = ~(1 | host_plant),
                  data = genus_mat_gam)

summary(genus_gam3$gam) # Sample date has strong relationship
plot(genus_gam3$gam)

##@@@

#### checking for trends with PERMANOVA:

genus_mat_species <- gut_genus_matrix %>% ungroup() %>% 
  select(Cannabis : Ulmus)

genus_mat_predictors <- gut_genus_matrix %>% ungroup() %>% 
  select(-Cannabis : -Ulmus)

# This model below makes more sense, I think this is the structure
# we're interested in. We expect the region to account for the variation
# in gut contents. Host plant should have a large effect but the effect is
# inflated because they also eat the host plant.
genus_ord_adonis1 <- adonis2(genus_mat_species ~
                            splines::ns(sample_date, df = 3) +
                            region + Year + BCTV,
                            strata = gut_genus_matrix$host_plant,
                          data = gut_genus_matrix)


gut_genus_matrix <- gut_genus_matrix %>% 
  mutate(year_time = case_when(
    Year == "2019" ~ sample_date,
    Year == "2020" ~ sample_date + 365,
    Year == "2021" ~ sample_date + (2*365),
    Year == "2022" ~ sample_date + (3*365),
    TRUE ~ NA
  ))

genus_ord_adonis2 <- adonis2(genus_mat_species ~
                            splines::ns(year_time, df = 3) +
                            region + BCTV,
                            strata = gut_genus_matrix$host_plant,
                          data = gut_genus_matrix)

```




```{r gut_sample_date_genus_figure_prep, echo = F, cache=F}


genus_sites <- data.frame(scores(gut_ord_genus)$sites) %>% 
  rownames_to_column("sample_num") %>% 
  bind_cols(., genus_mat_predictors)

genus_host_centroids <- genus_sites %>% 
  group_by(host_plant) %>% 
  summarise(NMDS1 = mean(NMDS1),
            NMDS2 = mean(NMDS2)) 

genus_ord_sample_date <- gam(sample_date ~ s(NMDS1, NMDS2, bs = "ts"),
                       data = genus_sites)

summary(genus_ord_sample_date)

preddat_genus <- expand.grid(NMDS1 = seq(-2, 2.3, 0.5),
                       NMDS2 = seq(-1.5, 2.5, 0.5),
                       Year = c(2019, 2020, 2021, 2022))
preddat_genus$date_pred <- predict(genus_gam3$gam,
                                 newdata = preddat_genus)


preddat_genus <- preddat_genus %>% 
  mutate(date_pred = case_when(
    Year == 2019 ~ date_pred,
    Year == 2020 ~ date_pred-365,
    Year == 2021 ~ date_pred-(2*365),
    Year == 2022 ~ date_pred-(3*365),
    TRUE ~ NA
  )) %>% 
  select(-Year) %>% 
  distinct() %>% 
  group_by(NMDS1, NMDS2) %>% 
  summarise(date_pred = mean(date_pred))



genus_species <- data.frame(scores(gut_ord_genus)$species) %>% 
  rownames_to_column("genus")




genus_species <- genus_species %>% 
  left_join(., genus_counts, by = "genus")

```


### Gut contents by sample date

```{r gut_sample_date_genus_fig, echo = F, cache=F}



ggplot(mapping = aes(x = NMDS1, y = NMDS2)) +
  geom_contour(data = preddat_genus,
               aes(z = date_pred), color = "grey") +
  metR::geom_text_contour(data = preddat_genus,
                          aes(z = date_pred),
                          color = "grey", stroke = 0.15, skip = 1) +
  geom_text_repel(data = genus_species, max.overlaps = 25,
                  aes(label = genus, size = total_counts)) +
  scale_size_binned(transform = "log10", range = c(1.5, 5),
             breaks = c(100, 200, 300, 400)) +
  theme_cowplot() +
  # geom_point(data = bee_sites,
  #            aes(x = NMDS1, y = NMDS2, color = period),
  #            show.legend = F) +
  labs(size = "Abundance")
```


### Genus by year

```{r gut_sample_date_year_genus_fig, echo = F, cache=F}

genus_year_centroids <- genus_sites %>% 
  group_by(Year) %>% 
  summarise(NMDS1 = mean(NMDS1),
            NMDS2 = mean(NMDS2)) 

ggplot(mapping = aes(x = NMDS1, y = NMDS2)) +
  geom_contour(data = preddat_genus,
               aes(z = date_pred), color = "grey") +
  metR::geom_text_contour(data = preddat_genus,
                          aes(z = date_pred),
                          color = "grey", stroke = 0.15, skip = 1) +
  geom_text_repel(data = genus_species, max.overlaps = 20,
                  aes(label = genus, size = total_counts)) +
  scale_size_binned(transform = "log10", range = c(1.5, 5),
             breaks = c(1000, 5000, 10000)) +
  theme_cowplot() +
  stat_ellipse(data = genus_sites,
               aes(x = NMDS1, y = NMDS2, color = Year),
               show.legend = F) +
  geom_point(data = genus_year_centroids,
             aes(x = NMDS1, y = NMDS2, fill = Year),
             shape = 21, size = 5) +
  # geom_point(data = bee_sites,
  #            aes(x = NMDS1, y = NMDS2, color = period),
  #            show.legend = F) +
  labs(size = "Abundance",
       fill = "Year",
       x = "NMDS1",
       y = "NMDS2") +
  scale_fill_viridis_d() +
  scale_color_viridis_d()

```

### Genus by month

```{r gut_sample_date__genus_fig, echo = F, cache=F}


genus_month_centroids <- genus_sites %>% 
  group_by(time_period) %>% 
  summarise(NMDS1 = mean(NMDS1),
            NMDS2 = mean(NMDS2)) 

ggplot(mapping = aes(x = NMDS1, y = NMDS2)) +
  geom_contour(data = preddat_genus,
               aes(z = date_pred), color = "grey") +
  metR::geom_text_contour(data = preddat_genus,
                          aes(z = date_pred),
                          color = "grey", stroke = 0.15, skip = 1) +
  geom_text_repel(data = genus_species, max.overlaps = 20,
                  aes(label = genus, size = total_counts)) +
  scale_size_binned(transform = "log10", range = c(1.5, 5),
             breaks = c(1000, 5000, 10000)) +
  theme_cowplot() +
  stat_ellipse(data = genus_sites,
               aes(x = NMDS1, y = NMDS2, color = time_period),
               show.legend = F) +
  geom_point(data = genus_month_centroids,
             aes(x = NMDS1, y = NMDS2, fill = time_period),
             shape = 21, size = 5) +
  # geom_point(data = bee_sites,
  #            aes(x = NMDS1, y = NMDS2, color = period),
  #            show.legend = F) +
  labs(size = "Abundance",
       fill = "Month") +
  scale_fill_viridis_d(direction = -1) +
  scale_color_viridis_d(direction = -1)


```

### Genus by field type

```{r gut_sample_date_host_genus_fig, echo = F, cache=F}



ggplot(mapping = aes(x = NMDS1, y = NMDS2)) +
  geom_contour(data = preddat_genus,
               aes(z = date_pred), color = "grey") +
  metR::geom_text_contour(data = preddat_genus,
                          aes(z = date_pred),
                          color = "grey", stroke = 0.15, skip = 1) +
  geom_text_repel(data = genus_species, max.overlaps = 20,
                  aes(label = genus, size = total_counts)) +
  scale_size_binned(transform = "log10", range = c(1.5, 5),
             breaks = c(1000, 5000, 10000)) +
  theme_cowplot() +
  stat_ellipse(data = genus_sites,
               aes(x = NMDS1, y = NMDS2, color = host_plant),
               show.legend = F) +
  geom_point(data = genus_host_centroids,
             aes(x = NMDS1, y = NMDS2, fill = host_plant),
             shape = 21, size = 5) +
  # geom_point(data = bee_sites,
  #            aes(x = NMDS1, y = NMDS2, color = period),
  #            show.legend = F) +
  labs(size = "Abundance",
       color = "Host plant",
       x = "NMDS1",
       y = "NMDS2") +
  scale_fill_viridis_d() +
  scale_color_viridis_d()



```



### Genus by regions

```{r gut_sample_date_region_genus_fig, echo = F, cache=F}

genus_region_centroids <- genus_sites %>% 
  group_by(region) %>% 
  summarise(NMDS1 = mean(NMDS1),
            NMDS2 = mean(NMDS2)) 

ggplot(mapping = aes(x = NMDS1, y = NMDS2)) +
  geom_contour(data = preddat_genus,
               aes(z = date_pred), color = "grey") +
  metR::geom_text_contour(data = preddat_genus,
                          aes(z = date_pred),
                          color = "grey", stroke = 0.15, skip = 0) +
  geom_text_repel(data = genus_species, max.overlaps = 25,
                  aes(label = genus, size = total_counts)) +
  scale_size_binned(transform = "log10", range = c(1.5, 5),
             breaks = c(1000, 5000, 10000, 20000)) +
  theme_cowplot() +
  stat_ellipse(data = genus_sites,
               aes(x = NMDS1, y = NMDS2, color = region),
               show.legend = F) +
  geom_point(data = genus_region_centroids,
             aes(x = NMDS1, y = NMDS2, fill = region),
             shape = 21, size = 5) +
  # geom_point(data = bee_sites,
  #            aes(x = NMDS1, y = NMDS2, color = period),
  #            show.legend = F) +
  labs(size = "Abundance",
       fill = "Region") +
  scale_fill_viridis_d() +
  scale_color_viridis_d()


```


### Genus by BCTV

```{r gut_sample_date_BCTV_genus_fig, echo = F, cache = F}

genus_bctv_centroids <- genus_sites %>% 
  group_by(BCTV) %>% 
  summarise(NMDS1 = mean(NMDS1),
            NMDS2 = mean(NMDS2)) 

ggplot(mapping = aes(x = NMDS1, y = NMDS2)) +
  geom_contour(data = preddat_genus,
               aes(z = date_pred), color = "grey") +
  metR::geom_text_contour(data = preddat_genus,
                          aes(z = date_pred),
                          color = "grey", stroke = 0.15, skip = 0) +
  geom_text_repel(data = genus_species, max.overlaps = 25,
                  aes(label = genus, size = total_counts)) +
  scale_size_binned(transform = "log10", range = c(1.5, 5),
             breaks = c(1000, 5000, 10000)) +
  theme_cowplot() +
  stat_ellipse(data = genus_sites,
               aes(x = NMDS1, y = NMDS2, color = BCTV)) +
  geom_point(data = genus_bctv_centroids,
             aes(x = NMDS1, y = NMDS2, fill = BCTV),
             shape = 21, size = 5, show.legend = F) +
  # geom_point(data = bee_sites,
  #            aes(x = NMDS1, y = NMDS2, color = period),
  #            show.legend = F) +
  labs(size = "Abundance",
       color = "BCTV") +
  scale_color_manual(values = c("#009E73",
                                "#CC79A7")) +
  scale_fill_manual(values = c("#009E73",
                                "#CC79A7"))


```


## Session Information

```{r Session_Info, echo = F, comment = ""}

# Add session information to help with reproduceability
sessionInfo()


```


