---
title: "Gut Contents Hemp, Hops, and Carrot"
author: "Riley M. Anderson"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
graphics: yes
output:
  github_document:
    toc: yes
    toc_depth: 5
    pandoc_args: --webtex
  html_document:
    keep_md: yes
    theme: readable
    mathjax: default
  html_notebook:
    code_folding: hide
    theme: readable
    mathjax: default
  pdf_document:
    toc: yes
header-includes:
  \usepackage{float}
  \floatplacement{figure}{H}
editor_options:
  chunk_output_type: console
---

```{r setup, include = F}
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
# @@@@@ Knitr Options
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@

# Set root directory to the project directory
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())


# Set default knitr options: 
# Suppress warnings and messages, cache chunks, 
#  set default figure size to 6x8 at 300 dpi, and save a png and pdf
knitr::opts_chunk$set(warning = F, message = F, collapse = T, cache = T,
    fig.height = 5, fig.width = 10, dpi = 300, # 6x8" @ 300dpi:1800x2400=4.3MP
    dev = 'png', dev.args = list(pdf = list(onefile = F)))

```



## Overview

Multivariate analyses of Camille's potato/hemp/hops/carrot BLH gut contents.
This analysis considers only presence/absence of plants, no assumptions of concentration are made.

### Summary of Results

* Plant species composition in the gut contents of BLH is weakly tied to sampling date (the grey contours in the NMDS figures).

* The predictors, **region**, and **BCTV** help explain some variation but do not differentiate gut composition. 

* **Host plant** was used as a block effect (random intercept and permutation stratification) in the models.

* The relationship with sampling date is convoluted and highly non-linear. I suspect this has much to do with the sampling across multiple years where regions were not sampled every year, or sampled at different times across years.

* The benchmark plant *Solanum*, for standardizing primer efficiency stands out by an order of magnitude. To me, this suggests that **sequences** are not representative of concentration in the gut. Instead, **sequences** are a function of primer efficiency. If so, this entire analysis should be ignored, as the ordinations are built from the assumption that **sequences** are at least partially a function of concentration in the gut.


```{r Main_Code, include = F, cache = F}

# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
# @@@@@ Setup - This code is run, but output is hidden
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@

# Load Packages
library(tidyverse) # Needed for data wrangling: dplyr, tidyr, ggplot2
library(cowplot) # Needed for publication-quality ggplots
library(vegan)
library(randomForest)
library(sjPlot)
library(ggrepel)
library(gamm4)

# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
# @@@@@ Data Preparation
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@

# Import datasets
# dat1 <- read.csv("data/BLH_gut_contents_2025.csv")

dat1 <- read.csv("data/gut_contents_full.csv")


set.seed(123)
```


```{r Data_Wrangling, echo = F, comment = ""}

dat1 <- dat1 %>% 
  filter(!is.na(BCTV),
         Year == 2022) %>% 
  mutate(Date = as.Date(Date, origin = "1899-12-30"),
         extraction_date = as.Date(extraction_date,
                                   origin = "1899-12-30"),
         across(c(BLH_ID, type, family, common_name, Terpene,
                genus, organism, primer, time_period,
                region, site_name, host_plant, BCTV), factor),
         Terpene = factor(case_when(
           Terpene == "" ~ "none",
           Terpene == "None" ~ "none",
           TRUE ~ Terpene
         ))) %>% 
  # correcting typos in time_period
  mutate(time_period = case_when(
    time_period == " August" ~ "August",
    time_period == " April" ~ "April",
    time_period == " July" ~ "July",
    time_period == " June" ~ "June",
    time_period == " March" ~ "March",
    time_period == " May" ~ "May",
    time_period == " October" ~ "October",
    TRUE ~ time_period),
         time_period = factor(time_period,
                              levels = c("March", "April", "May",
                                         "June", "July", "August",
                                         "October")))



meta <- dat1 %>% 
  select(BLH_ID, time_period, Date, extraction_date,
         region, host_plant, BCTV, Terpene, Year) %>% 
  distinct()

## Matrix and species by "Crop type":

species_counts <- dat1 %>% 
  group_by(BLH_ID, genus) %>% 
  tally() %>% 
  group_by(genus) %>% 
  summarise(total_counts = sum(n)) %>% 
  arrange(desc(total_counts)) %>% 
  filter(total_counts > quantile(total_counts, 0.8)) %>% 
  droplevels()


gut_matrix <- dat1 %>%
  semi_join(., species_counts, by = "genus") %>% 
  group_by(BLH_ID, genus) %>%
  tally() %>% 
  pivot_wider(names_from = genus,
              values_from = n,
              values_fill = list(n = 0)) %>% 
  left_join(., meta, by = "BLH_ID") %>% 
  mutate(sample_date = yday(Date),
         ex_date = yday(extraction_date)) %>% 
  select(-Date, -extraction_date)



```

## NMDS by genus
```{r NMDS_calcs_genus, echo = F, cache=F}

gut_ord <- gut_matrix %>% ungroup() %>% 
  select(Cannabis : Humulus) %>% 
  metaMDS(., k = 3, distance = "bray",
          trymax = 50, maxit = 1000)
## stress is fine with 3 dimensions

gut_ord$stress
stressplot(gut_ord)
plot(gut_ord)
# checking for trends with envfit():

gut_matrix <- gut_matrix %>% 
  mutate(Year = factor(Year))

gut_mod_envfit <- envfit(gut_ord ~ sample_date +
                           region + BCTV + Year,
                         strata = gut_matrix$host_plant,
                         choices = c(1:3),
                         data = gut_matrix, nperm = 999)

gut_mod_envfit # Only sample date matters

gut_mod_envfit <- envfit(gut_ord ~ sample_date + Year +
                           region + BCTV + host_plant,
                         choices = c(1:3),
                         data = gut_matrix, nperm = 999)

gut_mod_envfit # Only sample date matters



## checking for trends with GAM:

gut_mat_gam <- bind_cols(gut_matrix,
                           scores(gut_ord)$sites)


gam1 <- gamm4(log(sample_date) ~ s(NMDS1, NMDS2, k = 8),
                  random = ~(1 | host_plant),
                  data = gut_mat_gam)

summary(gam1$gam) # Sample date has crazy relationship
plot(gam1$gam)



#### checking for trends with PERMANOVA:

gut_mat_species <- gut_matrix %>% ungroup() %>% 
  select(Cannabis : Humulus)

gut_mat_predictors <- gut_matrix %>% ungroup() %>% 
  select(-Cannabis : -Humulus)


gut_ord_adonis1 <- adonis2(gut_mat_species ~
                            splines::ns(sample_date, df = 7) +
                             BCTV + region,
                            strata = gut_matrix$host_plant,
                          data = gut_matrix)

gut_ord_adonis1

```




```{r gut_sample_date_genus_figure_prep, echo = F, cache=F}


gut_sites <- data.frame(scores(gut_ord)$sites) %>% 
  rownames_to_column("sample_num") %>% 
  bind_cols(., gut_mat_predictors)


preddat <- expand.grid(NMDS1 = seq(-2, 2.3, 0.5),
                       NMDS2 = seq(-1.7, 2, 0.5))
preddat$date_pred <- exp(predict(gam1$gam, newdata = preddat))


gut_species <- data.frame(scores(gut_ord)$species) %>% 
  rownames_to_column("genus")

gut_species <- gut_species %>% 
  left_join(., species_counts, by = "genus")

```


### Gut contents by sample date

```{r gut_sample_date_fig, echo = F, cache=F}


ggplot(mapping = aes(x = NMDS1, y = NMDS2)) +
  geom_contour(data = preddat,
               aes(z = date_pred), color = "grey") +
  metR::geom_text_contour(data = preddat,
                          aes(z = date_pred),
                          color = "grey", stroke = 0.15, skip = 1) +
  geom_text_repel(data = gut_species, max.overlaps = 25,
                  aes(label = genus, size = total_counts)) +
  scale_size_binned(range = c(1.5, 5),
             breaks = c(50, 100, 300)) +
  theme_cowplot() +
  labs(size = "Abundance", color = "Sample date")
```



### Genus by month

```{r gut_sample_date_month_fig, echo = F, cache=F}


gut_month_centroids <- gut_sites %>% 
  group_by(time_period) %>% 
  summarise(NMDS1 = mean(NMDS1),
            NMDS2 = mean(NMDS2)) 

ggplot(mapping = aes(x = NMDS1, y = NMDS2)) +
  geom_contour(data = preddat,
               aes(z = date_pred), color = "grey") +
  metR::geom_text_contour(data = preddat,
                          aes(z = date_pred),
                          color = "grey", stroke = 0.15, skip = 1) +
  geom_text_repel(data = gut_species, max.overlaps = 20,
                  aes(label = genus, size = total_counts)) +
  scale_size_binned(range = c(1.5, 5),
             breaks = c(50, 150, 300)) +
  theme_cowplot() +
  stat_ellipse(data = gut_sites,
               aes(x = NMDS1, y = NMDS2, color = time_period),
               show.legend = F) +
  geom_point(data = gut_month_centroids,
             aes(x = NMDS1, y = NMDS2, fill = time_period),
             shape = 21, size = 5) +
  # geom_point(data = bee_sites,
  #            aes(x = NMDS1, y = NMDS2, color = period),
  #            show.legend = F) +
  labs(size = "Abundance",
       fill = "Month") +
  scale_fill_viridis_d(direction = -1) +
  scale_color_viridis_d(direction = -1)


```

### Genus by field type

```{r gut_sample_date_host_fig, echo = F, cache=F}

gut_host_centroids <- gut_sites %>% 
  group_by(host_plant) %>% 
  summarise(NMDS1 = mean(NMDS1),
            NMDS2 = mean(NMDS2)) 

ggplot(mapping = aes(x = NMDS1, y = NMDS2)) +
  geom_contour(data = preddat,
               aes(z = date_pred), color = "grey") +
  metR::geom_text_contour(data = preddat,
                          aes(z = date_pred),
                          color = "grey", stroke = 0.15, skip = 1) +
  geom_text_repel(data = gut_species, max.overlaps = 20,
                  aes(label = genus, size = total_counts)) +
  scale_size_binned(range = c(1.5, 5),
             breaks = c(50, 150, 300)) +
  theme_cowplot() +
  stat_ellipse(data = gut_sites,
               aes(x = NMDS1, y = NMDS2, color = host_plant),
               show.legend = F) +
  geom_point(data = gut_host_centroids,
             aes(x = NMDS1, y = NMDS2, fill = host_plant),
             shape = 21, size = 5) +
  # geom_point(data = bee_sites,
  #            aes(x = NMDS1, y = NMDS2, color = period),
  #            show.legend = F) +
  labs(size = "Abundance",
       color = "Host plant") +
  scale_fill_viridis_d() +
  scale_color_viridis_d()



```



### Genus by regions

```{r gut_sample_date_region_genus_fig, echo = F, cache=F}

gut_region_centroids <- gut_sites %>% 
  group_by(region) %>% 
  summarise(NMDS1 = mean(NMDS1),
            NMDS2 = mean(NMDS2)) 

ggplot(mapping = aes(x = NMDS1, y = NMDS2)) +
  geom_contour(data = preddat,
               aes(z = date_pred), color = "grey") +
  metR::geom_text_contour(data = preddat,
                          aes(z = date_pred),
                          color = "grey", stroke = 0.15, skip = 0) +
  geom_text_repel(data = gut_species, max.overlaps = 25,
                  aes(label = genus, size = total_counts)) +
  scale_size_binned(range = c(1.5, 5),
             breaks = c(50, 150, 300)) +
  theme_cowplot() +
  stat_ellipse(data = gut_sites,
               aes(x = NMDS1, y = NMDS2, color = region),
               show.legend = F) +
  geom_point(data = gut_region_centroids,
             aes(x = NMDS1, y = NMDS2, fill = region),
             shape = 21, size = 5) +
  # geom_point(data = bee_sites,
  #            aes(x = NMDS1, y = NMDS2, color = period),
  #            show.legend = F) +
  labs(size = "Abundance",
       fill = "Region") +
  scale_fill_viridis_d() +
  scale_color_viridis_d()


```


### Genus by BCTV

```{r gut_sample_date_BCTV_genus_fig, echo = F, cache = F}

gut_bctv_centroids <- gut_sites %>% 
  group_by(BCTV) %>% 
  summarise(NMDS1 = mean(NMDS1),
            NMDS2 = mean(NMDS2)) 

ggplot(mapping = aes(x = NMDS1, y = NMDS2)) +
  geom_contour(data = preddat,
               aes(z = date_pred), color = "grey") +
  metR::geom_text_contour(data = preddat,
                          aes(z = date_pred),
                          color = "grey", stroke = 0.15, skip = 0) +
  geom_text_repel(data = gut_species, max.overlaps = 25,
                  aes(label = genus, size = total_counts)) +
  scale_size_binned(range = c(1.5, 5),
             breaks = c(50, 150, 300)) +
  theme_cowplot() +
  stat_ellipse(data = gut_sites,
               aes(x = NMDS1, y = NMDS2, color = BCTV)) +
  geom_point(data = gut_bctv_centroids,
             aes(x = NMDS1, y = NMDS2, fill = BCTV),
             shape = 21, size = 5, show.legend = F) +
  # geom_point(data = bee_sites,
  #            aes(x = NMDS1, y = NMDS2, color = period),
  #            show.legend = F) +
  labs(size = "Abundance",
       color = "BCTV") +
  scale_color_manual(values = c("#009E73",
                                "#CC79A7")) +
  scale_fill_manual(values = c("#009E73",
                                "#CC79A7"))


```

## Random forest BCTV
```{r random_forest_mods, echo = F}

# rf_matrix <- gut_matrix %>% 
#   mutate(bctv = factor(case_when(
#     BCTV == "0" ~ "healthy",
#     BCTV == "1" ~ "infected",
#     TRUE ~ NA
#   )))
# 
# rf_mod1 <- randomForest(bctv ~ . -BLH_ID -Terpene -BCTV,
#                         data = rf_matrix,
#                         importance = T, nPerm = 999,
#                         proximity = T, na.action = na.omit)
# 
# levels(rf_matrix$BCTV)
# MDSplot(rf_mod1, gut_matrix$BCTV)

```


## Session Information

```{r Session_Info, echo = F, comment = ""}

# Add session information to help with reproduceability
sessionInfo()


```


