---
title: "BLH Gut Diversity in Potato"
author: "Riley M. Anderson"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
graphics: yes
output:
  github_document:
    toc: yes
    toc_depth: 5
    pandoc_args: --webtex
  html_document:
    keep_md: yes
    theme: readable
    mathjax: default
  html_notebook:
    code_folding: hide
    theme: readable
    mathjax: default
  pdf_document:
    toc: yes
header-includes:
  \usepackage{float}
  \floatplacement{figure}{H}
editor_options:
  chunk_output_type: console
---

```{r setup, include = F}
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
# @@@@@ Knitr Options
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@

# Set root directory to the project directory
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())


# Set default knitr options: 
# Suppress warnings and messages, cache chunks, 
#  set default figure size to 6x8 at 300 dpi, and save a png and pdf
knitr::opts_chunk$set(warning = F, message = F, collapse = T, cache = T,
    fig.height = 6, fig.width = 8, dpi = 300, # 6x8" @ 300dpi:1800x2400=4.3MP
    dev = c('png', 'pdf'), dev.args = list(pdf = list(onefile = F)))

```



## Overview

What is this analysis about?

### Summary of Results
* 

```{r Main_Code, include = F, cache = F}

# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
# @@@@@ Setup - This code is run, but output is hidden
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@

# Load Packages
library(tidyverse) # Needed for data wrangling: dplyr, tidyr, ggplot2
library(cowplot) # Needed for publication-quality ggplots
library(vegan)
library(emmeans)
library(glmmTMB)
library(sjPlot)
library(tidymodels)
library(ggridges)
library(knitr)

# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
# @@@@@ Data Preparation
# @@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@

# Import datasets
dat1 <- read.csv("data/gut_contents_full.csv")

crop_type <- read.csv("data/crop_types.csv")


# Functions

# function to calculate plant diversity at variaous scales:
plant_div_fun <- function(data, blh_id){
  data %>% 
    filter(BLH_ID = blh_id) %>% 
    group_by(genus) %>% 
    tally(name = "plant_count") %>% 
    pivot_wider(names_from = genus,
              values_from = plant_count,
              values_fill = list(plant_count = 0)) %>% 
    column_to_rownames("site") %>% 
    diversity()
}


# Function to check for overdispersion in poisson and binomial models:

overdispersion_test <- function(model, type = "pearson"){
    # Get the pearson residuals
    residuals <- resid(model, type = type)
    # Get the residual degrees of freedom of the model
    df <- df.residual(model)
    # Sum of residual deviance
    dev <- sum(residuals ^ 2)
    # Overdispersion = sum of squared residuals / residual degrees of freedom
    ratio <- round(dev / df, 3)
    # P-value 
    pvalue <- round(pchisq(dev, df, lower.tail = FALSE), 3)
    # Get the formula
    f = paste(as.character(formula(model))[2:3], collapse = " ~ ")
    # Get the model name
    name <- deparse(substitute(model))
    cat("Overdispersion ratio for model:", name, "\nformula:", f, 
        "\n\nAcceptable range: 1 - 1.4\nOverdispersion ratio:",
        ratio, " df:", df, " p =", pvalue, "\n", 
        ifelse(pvalue < 0.05, "Data are overdispersed\n", 
        "Data are not overdispersed\n"))
    # Return all the parameters
    return(c(ratio = ratio, deviance = dev, df = df, pvalue = pvalue))
}


# this function is useful for arranging ridge plots by time
Mode <- function(x) {
  # ensure input is a numeric vector
  if (!is.numeric(x)) {
    stop("Input must be a numeric vector.")
  }

  # create a table of frequencies
  freq_table <- table(x)

  # identify the maximum frequency
  max_freq <- max(freq_table)

  # extract the values that have the maximum frequency
  modes <- as.numeric(names(freq_table[freq_table == max_freq]))

  # return the first mode in case of ties (multimodality)
  return(modes[1])
}
```


```{r Data_Wrangling, echo = F, comment = ""}

dat1 <- dat1 %>% 
  filter(!is.na(BCTV),
         Year != 2022) %>% 
  mutate(Date = as.Date(Date, origin = "1899-12-30"),
         extraction_date = as.Date(extraction_date,
                                   origin = "1899-12-30"),
         across(c(BLH_ID, type, family, common_name, Terpene,
                genus, organism, primer, time_period, Year, CPt,
                region, site_name, host_plant, BCTV), factor),
         Terpene = factor(case_when(
           Terpene == "" ~ "none",
           Terpene == "None" ~ "none",
           TRUE ~ Terpene))
         # ,
         # host_plant = factor(case_when(
         #   host_plant == "Hemp" ~ "Hemp",
         #   host_plant == "Hops" ~ "Hops",
         #   host_plant == "Carrot" ~ "Carrot",
         #   TRUE ~ "Potato"
         # ), levels = c("Potato", "Carrot", "Hemp", "Hops"))
         ) %>% 
  # correcting typos in time_period
  mutate(time_period = case_when(
    time_period == " August" ~ "August",
    time_period == " April" ~ "April",
    time_period == " July" ~ "July",
    time_period == " June" ~ "June",
    time_period == " March" ~ "March",
    time_period == " May" ~ "May",
    time_period == " October" ~ "October",
    TRUE ~ time_period),
         time_period = factor(time_period,
                              levels = c("March", "April", "May",
                                         "June", "July", "August",
                                         "October")))


meta_dat <- dat1 %>% 
  select(-type : -blh_mix_count, -region_original,
         -Terpene, -extraction_date, -nucleic_acid,
         -purity, -quality, -S_citri, -site_name) %>% 
  filter(!is.na(CPt)) %>% 
  distinct() %>% 
  mutate(co_infected = factor(case_when(
    BCTV == "1" & CPt == "1" ~ "1",
    BCTV == "0" | CPt == "0" ~ "0",
    TRUE ~ NA)),
    Month = month(Date),
    sample_date = scale(yday(Date)))



richness <- dat1 %>% 
  group_by(BLH_ID) %>% 
  tally(name = "richness") %>% 
  left_join(., meta_dat, by = "BLH_ID")

richness <- richness %>% 
  mutate(nYear = as.numeric(Year) + 2018,
         BCTV = as.numeric(BCTV) - 1,
         CPt = as.numeric(CPt) - 1)

# plant_div <- levels(dat1$BLH_ID) %>% 
#   map(~ plant_div_fun(dat1, blh_id = .x))
# 
# names(plant_div) <- levels(dat1$BLH_ID)




```


# BCTV by richness
```{r bctv_richness, echo = F}

bctv_mod1 <- glmmTMB(BCTV ~ richness + (1 |region),
                   family = binomial(),
                   data = richness)

summary(bctv_mod1)

yhat_bctv1 <- emmeans(bctv_mod1, ~richness,
                      at = list(richness = seq(1, 20, 1)),
                      type = "response") %>% as.data.frame()

ggplot(richness, aes(x = richness)) +
  geom_ribbon(data = yhat_bctv1,
              aes(ymin = asymp.LCL, ymax = asymp.UCL),
              fill = "darkorange2", alpha = 0.4) +
  geom_line(data = yhat_bctv1,
            aes(y = prob), color = "darkorange2") +
  geom_jitter(aes(y = BCTV, fill = Year), width = 0.4, height = 0.02,
              shape = 21) +
  scale_fill_viridis_d(direction = -1) +
  theme_bw(base_size = 16) +
  labs(x = "Gut species richness",
       y = "Probability of BCTV")



```

* Simple models show a robust effect of gut species richness on BCTV infection ($\beta$ = -0.16, SE = 0.05, *P* < 0.001, AIC = `r round(AIC(bctv_mod1),2)`. This effect is independent of region. That is, each region has varying levels of BCTV infection, but the effect of richness does not vary by region.

* However, there may be an effect of **year** on the variation in BCTV. In the plot above, the raw data are shown and colored by year with 2019 in yellow, 2020 in blue, and 2021 in purple. Let's have a detailed look below:

```{r bctv_year, echo = F}

bctv_mod2 <- glmmTMB(BCTV ~ Year + (1 |region),
                   family = binomial(),
                   data = richness)
summary(bctv_mod2)

yhat_bctv2 <- emmeans(bctv_mod2, ~ Year,
                      at = list(seq(2019, 2021, 1)),
                      type = "response") %>% as.data.frame()

ggplot(richness, aes(x = Year)) +
  geom_errorbar(data = yhat_bctv2,
              aes(ymin = asymp.LCL, ymax = asymp.UCL),
              width = 0.1, show.legend = F) +
  geom_point(data = yhat_bctv2,
            aes(y = prob),
            size = 3, show.legend = F) +
  geom_jitter(aes(y = BCTV, fill = Year),
              shape = 21, width = 0.3,
              alpha = 0.8, height = 0.01, show.legend = F) +
  theme_bw(base_size = 16) +
  scale_fill_viridis_d(direction = -1) +
  scale_color_viridis_d(direction = -1) +
  labs(y = "Probability of BCTV",
       x = "Year")


```

* Okay, so 2019 had much lower levels of BCTV, relative to 2020 and 2021. Moreover, **year** is a better predictor of BCTV than **richness** (AIC = `r round(AIC(bctv_mod2),2)`)

* Did gut species richness also vary across years? Let's find out:


```{r richness_year, echo = F}

richness_mod1 <- glmmTMB(richness ~ Year + (1 |region),
                   family = nbinom2(),
                   data = richness)

overdispersion_test(richness_mod1)

summary(richness_mod1)

yhat_richness <- emmeans(richness_mod1, ~ Year,
                         at = list(seq(2019, 2021, 1)),
                         type = "response") %>% as.data.frame()

ggplot(richness, aes(x = Year)) +
  geom_errorbar(data = yhat_richness,
              aes(ymin = asymp.LCL, ymax = asymp.UCL),
              width = 0.1, show.legend = F) +
  geom_point(data = yhat_richness,
            aes(y = response),
            size = 3, show.legend = F) +
  geom_jitter(aes(y = richness, fill = Year),
              shape = 21, width = 0.3,
              alpha = 0.6, height = 0.3, show.legend = F) +
  theme_bw(base_size = 16) +
  scale_fill_viridis_d(direction = -1) +
  scale_color_viridis_d(direction = -1) +
  labs(y = "Gut species richness",
       x = "Year")



```

* Yes, gut species richness varies significantly across years, with richness declining over time. This evidence suggests that **richness** and **year** are both important predictors of BCTV. Is this because they are collinear? Or do they each contribute to model fit?

* This is not the same as a statistical interaction. When two independent variables are collinear, we may be fooled into thinking one is significant when in reality, its significance comes from its proxy as the other.

* Test for collinearity and model fit with AIC:

```{r bctv_richness_and_year, echo = F}



bctv_mod3 <- glmmTMB(BCTV ~ richness + nYear +
                     (1 | region),
                   family = binomial(),
                   data = richness)



# checking for collinearity:
cov2cor(vcov(bctv_mod3)$cond) # not bad.

summary(bctv_mod3)


yhat_bctv <- emmeans(bctv_mod3, ~ richness + nYear,
                     at = list(richness = seq(1, 20, 1),
                               nYear = seq(2019, 2021, 1)),
                     type = "response") %>% as.data.frame()

ggplot(richness, aes(x = richness)) +
  geom_ribbon(data = yhat_bctv,
              aes(ymin = prob - SE, ymax = prob + SE,
                  fill = factor(nYear), group = nYear),
              alpha = 0.4, show.legend = F) +
  geom_line(data = yhat_bctv,
            aes(y = prob, color = factor(nYear)),
            show.legend = F) +
  geom_jitter(aes(y = BCTV, fill = factor(nYear)),
              shape = 21, width = 0.4, height = 0.02) +
  theme_bw(base_size = 16) +
  scale_fill_viridis_d(direction = -1) +
  scale_color_viridis_d(direction = -1) +
  labs(y = "Probability of BCTV",
       x = "Gut species richness",
       fill = "Year")

```

* Correlation between **year** and **richness** is weak (*r* = `r round(cov2cor(vcov(bctv_mod3)$cond)[2,3], 2)`), so no collinearity. However,
including **year** in the model loses the **richness** effect.

* We've now fit three versions of models to predict BCTV. Lets compare with AIC and decide which model to use:

```{r AIC_bctv_models, echo = T}

AIC(bctv_mod1, bctv_mod2, bctv_mod3)

```

* Model selection with AIC suggests the model with **year** alone is the best predictor. 

* This means that our evidence of the dilution effect in BCTV is weak. Probably should not make this the main point of the paper.



# CPt by richness
```{r CPt_richness_year_fig, echo = F}


cpt_mod1 <- glmmTMB(CPt ~ richness + Year +
                    (1 | region),
                  family = binomial(),
                  data = richness)

summary(cpt_mod1)

yhat_cpt <- emmeans(cpt_mod1, ~richness,
                    at = list(richness = seq(1, 20, 1)),
                    type = "response") %>% as.data.frame()

ggplot(richness, aes(x = richness)) +
  geom_ribbon(data = yhat_cpt,
              aes(ymin = asymp.LCL, ymax = asymp.UCL),
              fill = "darkorange2", alpha = 0.4) +
  geom_line(data = yhat_cpt,
            aes(y = prob), color = "darkorange2") +
  geom_jitter(aes(y = CPt, fill = Year),
              width = 0.4, height = 0.02, shape = 21) +
  scale_fill_viridis_d(direction = -1) +
  theme_bw(base_size = 16) +
  labs(x = "Gut species richness",
       y = "Probability of CPt")


```

* Both **richness** and **year** have no effect on CPt infection (*P* > 0.5).

# Proportion plants infected

```{r plant_inf_props, echo = F, fig.width=11, fig.height=5}

dat1 %>% 
  semi_join(., crop_type, by = "genus") %>% 
  mutate(BCTV = as.numeric(BCTV) - 1,
         CPt = as.numeric(CPt) - 1,
         co_infected = (case_when(
                        BCTV == 1 & CPt == 1 ~ 1,
                        BCTV != 1 | CPt != 1 ~ 0)),
         healthy = case_when(
                        BCTV == 0 & CPt == 0 ~ 1,
                        TRUE ~ 0)) %>% 
  group_by(genus, BCTV, CPt, co_infected, healthy) %>% 
  tally() %>%
  mutate(status = case_when(
    healthy == 1 ~ "healthy",
    CPt == 1 & co_infected == 0 ~ "CPt",
    BCTV == 1 & co_infected == 0 ~ "BCTV",
    co_infected == 1 ~ "co infected"
  )) %>% 
  select(-BCTV : -healthy) %>% 
  left_join(., crop_type, by = "genus") %>% 
  mutate(crop_type = case_when(
    crop_type == "crop" ~ "Crops",
    crop_type == "non crop" ~ "Non crops",
    crop_type == "tree" ~ "Trees"
  )) %>% 
  ggplot(aes(x = genus, y = n,
             fill = factor(status,
                           level = c("healthy", "BCTV",
                                      "CPt", "co infected")))) +
  geom_bar(stat = "identity") +
  facet_wrap(~ crop_type, scales = "free") +
  coord_flip() +
  theme_bw() +
  scale_fill_viridis_d(option = "G", direction = -1) +
  theme(legend.title = element_blank(),
        strip.background = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())

```

# Plants in the gut over time

```{r plants_in_gut_time, echo = F}

genus_orders <- dat1 %>% 
  semi_join(., crop_type, by = "genus") %>% 
  mutate(Week = week(Date)) %>% 
  group_by(genus) %>% 
  summarise(peak = Mode(Week)) %>% 
  arrange(desc(peak)) %>% data.frame() %>% 
  left_join(., crop_type, by = "genus")

crop_orders <- genus_orders %>% filter(crop_type == "crop") %>%
  droplevels() %>% 
  arrange(desc(peak)) %>% 
  select(genus)

crop_orders <- crop_orders$genus

non_crop_orders <- genus_orders %>% filter(crop_type == "non crop") %>%
  droplevels() %>% 
  arrange(desc(peak)) %>% 
  select(genus)

non_crop_orders <- non_crop_orders$genus

tree_orders <- genus_orders %>% filter(crop_type == "tree") %>%
  droplevels() %>% 
  arrange(desc(peak)) %>% 
  select(genus)

tree_orders <- tree_orders$genus

```


## Crops by time
```{r crop_time, echo = F}

dat1 %>%
  semi_join(., crop_type, by = "genus") %>% 
  left_join(., crop_type, by = "genus") %>% 
  filter(crop_type == "crop",
         genus != "Coriandrum" & genus != "Pisum" &
           genus != "Capsicum" & genus != "Cucurbita" &
           genus != "Spinacia") %>%
  droplevels() %>% 
  mutate(Week = week(Date)) %>%
  ggplot(aes(x = Week,
             y = factor(genus, level = crop_orders),
             fill = genus)) +
  geom_density_ridges(aes(height = stat(density)),
                      scale = 4,
                      rel_min_height = 0.01,
                      stat = "density",
                      bw = "nrd0") +
  theme_ridges(grid = F) +
  theme(legend.position = "none") +
  scale_x_continuous(breaks = c(15, 25, 35),
                     labels = c("27 March",
                                "5 June",
                                "14 August")) +
  labs(x = "", y = "") +
  geom_vline(xintercept = 27.3,
             color = "grey50", linetype = "dashed") +
  annotate(geom = "text", x = 13, y = 9, label = " ") +
  annotate(geom = "text", x = 36, y = 9, label = " ") +
  annotate(geom = "text", x = 16, y = 8, label = "Spring",
           size = 5) +
  annotate(geom = "text", x = 32, y = 8, label = "Summer",
           size = 5) +
  scale_fill_viridis_d(option = "A")

```

## Non-crops by time
```{r non_crop_time, echo = F}

dat1 %>%
  semi_join(., crop_type, by = "genus") %>% 
  left_join(., crop_type, by = "genus") %>% 
  filter(crop_type == "non crop") %>% 
  droplevels() %>% 
  mutate(Week = week(Date)) %>%
  ggplot(aes(x = Week,
             y = factor(genus, level = non_crop_orders),
             fill = genus)) +
  geom_density_ridges(aes(height = stat(density)),
                      scale = 4,
                      rel_min_height = 0.01,
                      stat = "density",
                      bw = "nrd0") +
  theme_ridges(grid = F) +
  theme(legend.position = "none") +
  scale_x_continuous(breaks = c(15, 25, 35),
                     labels = c("27 March",
                                "5 June",
                                "14 August")) +
  labs(x = "", y = "") +
  geom_vline(xintercept = 27.3,
             color = "grey50", linetype = "dashed") +
  annotate(geom = "text", x = 13, y = 15, label = " ") +
  annotate(geom = "text", x = 36, y = 15, label = " ") +
  annotate(geom = "text", x = 16, y = 14, label = "Spring",
           size = 5) +
  annotate(geom = "text", x = 32, y = 14, label = "Summer",
           size = 5) +
  scale_fill_viridis_d(option = "B")

```

## Trees by time
```{r tree_time, echo = F}

dat1 %>%
  semi_join(., crop_type, by = "genus") %>% 
  left_join(., crop_type, by = "genus") %>% 
  filter(crop_type == "tree",
         genus != "Salix") %>%
  droplevels() %>% 
  mutate(Week = week(Date)) %>%
  ggplot(aes(x = Week,
             y = factor(genus, level = tree_orders),
             fill = genus)) +
  geom_density_ridges(aes(height = stat(density)),
                      scale = 4,
                      rel_min_height = 0.01,
                      stat = "density",
                      bw = "nrd0") +
  theme_ridges(grid = F) +
  theme(legend.position = "none") +
  scale_x_continuous(breaks = c(15, 25, 35),
                     labels = c("27 March",
                                "5 June",
                                "14 August")) +
  labs(x = "", y = "") +
  geom_vline(xintercept = 27.3,
             color = "grey50", linetype = "dashed") +
  annotate(geom = "text", x = 13, y = 14, label = " ") +
  annotate(geom = "text", x = 36, y = 14, label = " ") +
  annotate(geom = "text", x = 16, y = 13, label = "Spring",
           size = 5) +
  annotate(geom = "text", x = 32, y = 13, label = "Summer",
           size = 5) +
  scale_fill_viridis_d(option = "C")

```

## Session Information

```{r Session_Info, echo = F, comment = ""}

# Add session information to help with reproduceability
sessionInfo()


```


